\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Rohan Honwade}


\section{Objective}
Looking for Full-Time opportunities in areas such as 
Backend Application development, Machine Learning, Analytics, Tool development

\section{Work experience}
\begin{eventlist}
\item{July 2015 -- Present}
     {Oracle, Seattle, USA}
     {Senior Software Engineer}
     
Built the Generic Data Ingest feature using Scala, Akka Actors to ingest and process log files and insert this data into Apache Kafka, Apache HBase.\\ 

Deployed service as a Docker container\\ 
\resultwas{Successfully delivered POC version of the feature}

\item{May 2014 -- August 2014}
     {Amazon.com, Seattle, USA}
     {Software Development Engineer Intern}

%Top 10 Products Web Service :\\
Developed a Spring based Java web service using Service Oriented Architecture to provide the top 10 products bought by customers. Implemented Factory, Singleton design patterns.\\

%Amazon Home Page Widget : \\
Also developed a widget for the Amazon home page to consume this service


\item{April 2011 -- July 2013}
     {Oracle, Bangalore, India}
     {Senior Member of Technical Staff}

Wrapper around Selenium framework for user interface automation. Used Page Object design pattern.\\
\resultwas{Saved 90 hours of manual effort per release. Increase in automation from 0 to around 90\%}\\

Single point of contact for product feature. Spotted security vulnerabilities. Worked in an Agile methodology driven environment.

\item{July 2009 -- March 2011}
     {Misys PLC, Bangalore, India}
     {Software Engineer}

Java application to enforce coding standards upon file save. Used Factory design pattern.\\
\resultwas{Attached as a pre-commit hook in Subversion. Used by more than 150 developers}\\

Web application using JSP, Hibernate and Servlets to maintain metadata and relationship details of source code files.\\

Source code refactoring Java application. Made batch mode changes to 1500 files.\\
\resultwas{Saved 95\% of manual effort. New tool creation time reduced by 50\% using generic templates}\\
\end{eventlist}



\personal
    [www.linkedin.com/in/honwade]
    {320 Cedar Street, Apt 215, Seattle, USA}
    {+1 412-313-3587}
    {rhonwade@alumni.cmu.edu}
    {www.github.com/rhcode}
    {www.rhonwade.blogspot.com}

\section{Projects}

\begin{itemize}

\item\textbf{Machine Learning driven cloud workload usage prediction}\\
     %{Resource auto-scaling for Apache Mesos}
     % {Prediction of resource usage of applications deployed in cloud containers using past performance data}
     {Working on prediction of resource usage of applications deployed in cloud containers - an autoscaling service for Apache Mesos}
\item\textbf{Service placement in cloud using \\Machine Learning}\\
     {Effective placement of computation in a network for optimal usage of resources. Developed fitness function 
used for Genetic Algorithm}

\item\textbf{Stock Market Game (In progress)}\\
Game to simulate stock market portfolios. Using Scala Play Framework, Akka actors, MongoDB

\item\textbf{Android app for deal notification}\\
     {Connecting shops with users for location aware user preferred deals}\\
     Won a \$1000 {\highlighttext{Best Project Award}} out of 20 teams, from School of Computer Science, CMU

\item\textbf{Steganography Using Sudoku Puzzle}\\
     {Sudoku puzzles used as keys to hide data in images.
     \highlighttext{Best Research Paper Award}}

\end{itemize}

\section{Education}

{\hfill\sc Aug 2013 - May 2015}\\
\textbf{Carnegie Mellon University}\\ 
Master of Science in Information Technology\\
CIT, Pittsburgh, PA - Silicon Valley, CA, USA\\
GPA - 3.65\\
Select coursework - Machine Learning, Software Engineering, Mobile and Pervasive Computing Services\\

{\hfill\sc June 2005 - July 2009}\\
\textbf{RV College of Engineering}\\
Bachelor of Engineering in Computer Science\\
Visvesvaraya Technological University, India\\
GPA - 71/100\\
Select coursework - Algorithm Design and Analysis, Data Structures, Database Systems, Java\\ 


\vspace{-0.2in}
\section{Software skills}
\begin{factlist}
\item{Proficient}
     {Core Java}       

\item{Intermediate}
     {Scala, Akka, Spring, Hibernate, Machine Learning, Android, Unix, Shell scripting, MySQL, Git}

\item{Basic level}
     {Matlab, R, JavaScript, C++, C}
\end{factlist}

\end{document}

